\section{IMU}
The IMU \ref{trm::imu} that was present on WTR before, the MPU6050, was broken when the current group started work on the project.
As such, a replacement had to be chosen.
Rather than go with a 6-axis IMU like the MPU6050, a 9-axis IMU seemed like the better option, so an analysis was done to determine the best device.

The demands were as follows:
\begin{enumerate}
\item Device must have an accelerometer, gyroscope and magnetometer
\item Device must be Arduino/Pi compatible
\item Device must be affordable within the budget given by the product owner
\item Device must be accurate enough to contribute to the solution
\end{enumerate}

The following devices were selected as potentially viable options:
\begin{enumerate}
\item \href{https://www.sparkfun.com/products/13762}{MPU9250}- Sparkfun breakout
\item \href{https://store.arduino.cc/9-axis-motion-shield}{BNO055} - Arduino motionshield
\item \href{https://learn.adafruit.com/nxp-precision-9dof-breakout/overview}{NXP} - Adafruit breakout
\end{enumerate}

Each device has its features outlined in the following table:

\begin{table}[h]
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    \textbf{device} & \textbf{cost} & \textbf{operating voltage $V$} & \textbf{angular scale $^O /sec$} & \textbf{acceleration scale $G$}  & \textbf{format} \\ \hline
    MPU9250 & \$ 14,95 & 2.4 - 3.6 & 250 - 2000 & 2 - 16 & breakout board \\ \hline
    BNO055  & \$ 23,95 & 2.4 - 3.6 & 250 - 2000 & 2 - 16 & Arduino Shield \\ \hline
    NXP     & \$ 14,95 & 2 - 3.6   & 250 - 2000 & 2 - 8   & breakout board \\ \hline
    \end{tabular}
\caption{comparison of features of the three selected 9-axis IMU's}
\label{tbl::IMUcomp}
\end{table}

The three sensors here are fairly similar, though there are a few critical differences.
The MPU9250 and the NXP are very similar, and even have the same price.
Out of those 2, the MPU has a slightly higher range in the acceleration scale category, which for no added price, meaning it knocks out the NXP.
The MPU9250 and the BNO055 have the same sensitivity, but the price of the BNO055 is significantly higher than the MPU9250.
Therefore, the logical conclusion is that the MPU9250 should be used.

Figures were obtained from the following places:
\begin{itemize}
\item MPU9250 - \cite{mpu}
\item BNO055  - \cite{bno}
\item NXP - \cite{nxp1} , \cite{nxp2}
\end{itemize}

\newpage    
    